Problem 1.4

### 2020-01-18 mstemc/index.tex
finish the figures in prob1.4

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
\author{Eason}
\date{\today}
\title{signals and systems chapter 1 problems}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={signals and systems chapter 1 problems},
 pdfkeywords={},
 pdfsubject={summary of this post},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

 \thispagestyle{empty}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge signal and system chapter 1 problems} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
 \end{center}
 \endgroup

@@

\section{Basic Problems With Answers}
\label{sec:orgf4c241b}

\begin{prob}
Problem 1.1: Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
\begin{equation*}
\begin{array}{ccc}
 \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
 e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
 \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-i9\pi/4}  & \sqrt{2} e^{-i\pi/4}
\end{array}
\end{equation*}
\label{prob11}
\end{prob}

\begin{prob}
Problem 1.2: Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
-\pi < \theta \leq \pi\)):
\begin{equation*}
\begin{array}{c{3cm}c{3cm}c{3cm}}
5 & -2 & -3i \\
\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
\end{array}
\end{equation*}
\label{prob12}
\end{prob}

@@

In the end of \hyperref[prob11]{Problem 1.1} and \hyperref[prob11]{Problem 1.1}, I want to say
more about expressing \(\tfrac{1+i}{1-i}\) in its polar form. There are two
methods to get the polar form:
\begin{enumerate}
\item multiply the fraction's numerator and denominator by \(( 1 + i )\)

@@

\begin{eqnarray*}
\frac{1+i}{1-i} &=& \frac{\sqrt{2}e^{i\pi/4}}{\sqrt{2}e^{-i\pi/4}}  \\
&=& e^{i2\pi/4} = e^{i\pi/2} = i
\end{eqnarray*}
\end{enumerate}
\end{document}

>>>>

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
\author{Eason}
\date{\today}
\title{Signals and Systems Chapter 1 Problems}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Signals and Systems Chapter 1 Problems},
 pdfkeywords={},
 pdfsubject={summary of this post},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

 \thispagestyle{empty}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Signal and System Chapter 1 Problems} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
 \end{center}
 \endgroup

@@

\section{Basic Problems With Answers}
\label{sec:org66bb87c}

\subsection{Problem 1.1 and Problem 1.2}
\label{sec:org2a3de1e}

\begin{prob}[]{prob:1.3}
Problem 1.1: Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
\begin{equation*}
\begin{array}{ccc}
 \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
 e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
 \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-i9\pi/4}  & \sqrt{2} e^{-i\pi/4}
\end{array}
\end{equation*}
\label{prob11}
\end{prob}

\begin{prob}[]{prob:1.3}
Problem 1.2: Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
 -\pi < \theta \leq \pi\)):
\begin{equation*}
\begin{array}{c{3cm}c{3cm}c{3cm}}
5 & -2 & -3i \\
\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
\end{array}
\end{equation*}
\label{prob12}
\end{prob}

@@

In the end of \hyperref[prob11]{Problem 1.1} and \hyperref[prob12]{Problem 1.2}, I want to say
more about expressing \(\tfrac{1+i}{1-i}\) in its polar form. There are two
methods to get the polar form:
\begin{enumerate}
\item multiply the fraction's numerator and denominator by \(( 1 + i )\)

@@

\begin{eqnarray*}
\frac{1+i}{1-i} &=& \frac{\sqrt{2}e^{i\pi/4}}{\sqrt{2}e^{-i\pi/4}}  \\
&=& e^{i2\pi/4} = e^{i\pi/2} = i
\end{eqnarray*}
\end{enumerate}
\subsection{Problem 1.3}
\label{sec:orge16e8d1}

\begin{prob}[]{prob:1.3}
Problem 1.3: Determine the values of \(P_{\infty}\) and \(E_{\infty}\) for each
of the following signals:
\begin{equation*}
\begin{array}{ll}
\mathrm{(a)} \quad x_{1}(t) = e^{-2t}u(t) & \mathrm{(b)} \quad x_{2}(t) = e^{i(2t + \pi/4)} \\
 \mathrm{(c)} \quad x_{3}(t) = \cos(t) & \mathrm{(d)} \quad x_{1}[n] = (\tfrac{1}{2})^{n} u[n] \\
 \mathrm{( e )} \quad x_{2}[n] = e^{i(\pi/2n + \pi/8)} & \mathrm{(f)} \quad x_{3}[n] = \cos(\tfrac{\pi}{4}n)
\end{array}
\end{equation*}
\label{prob13}
\end{prob}

Before solving this problem, let's review the definition of \(P_{\infty}\) and
\(E_{\infty}\). For a continuous time signal \(x(t)\), we have
\begin{eqnarray}
\label{eq:2}
E_{\infty}&=& \lim_{T\to \infty} \int_{-T}^{T} |x(t)|^{2}\mathrm{d}t \\
P_{\infty}&=& \lim_{T\to \infty} \frac{1}{2T}\int_{-T}^{T} |x(t)|^{2}\mathrm{d}t = \lim_{T\to\infty} \frac{E_{\infty}}{2T}
\end{eqnarray}
For a discrete time signal \(x[n]\), we have:
\begin{eqnarray}
\label{eq:3}
E_{\infty}&=& \lim_{N\to \infty} \sum_{n=-N}^{+N} |x[n]|^{2} \\
P_{\infty}&=& \lim_{N\to \infty} \frac{1}{2N+1} \sum_{n=-N}^{+N} |x[n]|^{2} = \lim_{N\to\infty} \frac{E_{\infty}}{2N+1}
\end{eqnarray}

Equation (\ref{eq:2})(\ref{eq:3}) are not only mathmatical definitions but also
related to physical quantities such as power and energy in a physical system.
For an electric circuit, taking the voltage \(v(t)\) and current \(i(t)\) across
a resistor for example, the power at time \(t\) can be calculated by:
\begin{equation}
\label{eq:4}
p(t) = v(t)i(t) = \frac{v^{2}(t)}{R}
\end{equation}
Let's go back to equation (\ref{eq:2}) and equation(\ref{eq:3}), if
\(E_{\infty}< \infty\) we say that the signal has finite energy otherwise
infinite energy. If \(P_{\infty} <\infty\) we say that the signal has finite
power otherwise infinite power.

Next let's determine the values of \(P_{\infty}\) and \(E_{\infty}\) for the
given signals.

\(\mathbf{(a)}: x_{1}(t)= e^{-2t}u(t)\) :

\begin{eqnarray*}
E_{\infty}  & =  & \int_{\infty}^{\infty} |e^{-2t}u(t)|^{2} \mathrm{d}t \\
&=& \int_{0}^{\infty} e^{-4t} \mathrm{d}t \\
&=& \frac{1}{4}
\end{eqnarray*}
So, it's straightforward that:
\begin{equation}
\label{eq:5}
P_{\infty} = \lim_{T\to \infty} \frac{E_{\infty}}{2T}  = 0
\end{equation}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3.pdf}
\end{center}

\(\mathbf{(b)}: x_{2}(t)= e^{i(2t+\pi/4)}\)

We have \(|e^{i(2t+\pi/4)}| = 1\) , therefore
\begin{eqnarray*}
E_{\infty}&=& \int_{\infty}^{\infty} |x_{2}(t)= e^{i(2t+\pi/4)}|^{2} \mathrm{d}t \\
&=& \infty
\end{eqnarray*}

For power \(P_{\infty}\), we have:
\begin{eqnarray*}
P_{\infty}&= &\lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{2}(t)|^{2} \mathrm{d}t  \\
&=& 1
\end{eqnarray*}

This signal has constant power. If you keep the concept of rotation mentioned in
Problem \ref{prob11}, you will notice immediately that all the points generated by
\(x_{2}(t)\) lies on the unit circle.

\(\mathbf{(c)}:x_{3}(t)=\cos(t)\)

\begin{eqnarray*}
E_{\infty}&=& \lim_{T\to\infty} \int_{-\infty}^{\infty} |x_{3}(t)|^{2} \mathrm{d}t \\
&=& \int_{\infty}^{\infty} \cos(t)^{2} \mathrm{d}t = \infty
\end{eqnarray*}

\begin{eqnarray*}
P_{\infty}&=& \lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{3}(t)|^{2} \mathrm{d}t  \\
&=& \lim_{T\to\infty} \int_{-T}^{T} \cos(t)^{2} \mathrm{d}t \\
&=& \lim_{T\to\infty}  \int_{-T}^{T} \frac{1+\cos(2t)}{2} \mathrm{d}t = \frac{1}{2}
\end{eqnarray*}

\subsection{Problem 1.4}
\label{sec:org719025d}

\begin{prob}[]{prob:1-4}
 Problem 1.4: Let \(x[n]\) be a signal with \(x[n]=0\) for\(n< -2\) and \(n>4\),
for each signal given below, determine the values of \(n\) for which it is
guaranteed to be zero.
\begin{eqnarray*}
\mathbf{ (a) } & & x[n-3] \\
\mathbf{ (b) } & & x[n+4] \\
\mathbf{ (c) } & & x[-n]  \\
\mathbf{ (d) } & & x[-n+2] \\
\mathbf{ (e) } & & x[-n-2]
\end{eqnarray*}
\label{prob:1-4}
\end{prob}

For the given signals \(\mathbf{(a)}\) to \(\mathbf{(e)}\), the transformations
of the variable \(n\) will change the interval in which the signals are zero.
For the convenience of calculation, we write the origin signal as:
\begin{equation*}
x[m] = 0, m< -2 \quad \mathrm{and} \quad m>4
\end{equation*}

We can visualize \(x(m)\) as below (I just give an example, you can name any
signal that satisfy \(x[m] = 0, m< -2 \ \mathrm{and} \ m>4\)):

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4.pdf}
\end{center}

\(\mathbf{(a)}:x[n-3]\)

For signal \(\mathbf{(a)}\), to get the interval where \(x[n-3] = 0\), we have:
\begin{eqnarray*}
  t=n-3 &<& -2 \\
  t=n-3 &>& 4
\end{eqnarray*}
 Then, we have \(n < 1 \ \mathrm{and} \ n > 7\) from which we can see that
the new signal is a right shift three relative to the origin signal, i.e. new
signal is delayed with three.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4a.pdf}
\end{center}

\(\mathbf{(b)}:x[n+4]\)

For signal \(\mathbf{(b)}\), we have:
\begin{eqnarray*}
t=n+4&<&-2 \\
t=n+4&>&4
\end{eqnarray*}
Then, we have \(n<-6\ \mathrm{and}\ n>0\) from which we can see that the new
signal is a left shift four relative to the origin singal, i.e. new
signal is advanced with four.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4b.pdf}
\end{center}

\(\mathbf{(c)}: x[-n]\)

For signal \(\mathbf{( c )}\), we have:
\begin{eqnarray*}
t=-n&<&-2 \\
t=-n&>&4
\end{eqnarray*}

Then, we have \(n>2\ \mathrm{and} \ n<-4\) from which we can see that the new
signal is a reversal of the origin signal.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4c.pdf}
\end{center}

\(\mathbf{(d)}: x[-n+2]\)

for signal \(\mathbf{(d)}\), we have:
\begin{eqnarray*}
t=-n+2&<&-2 \\
t=-n+2&>&4
\end{eqnarray*}
Then, we have \(n>4\ \mathrm{and}\ n<-2\). For \(x[-n+2]\), we can first
flip the original signal then right shift the flipped signal by 2. Notice the
contents in the brackets \(-(n+2)\). I would like treat it as \(-(n-2)\), by
which I know that the minus symbol means reversal and \(-2\) means right
shift by 2.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4d.pdf}
\end{center}

\(\mathbf{(e)}: x[-n-2]\)

For signal \(\mathbf{(e)}\), we have:

\begin{eqnarray*}
t=-n-2&<&-2 \\
t=-n-2&>&4
\end{eqnarray*}

Then, we have \(n>0 \ \mathrm{and}\ n<-6\). To get the new signal, we have
to filp the original signal first then left shift the flipped signal by two.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4e.pdf}
\end{center}
\end{document}

### 2020-01-18 mstemc/mstemc.tex
finish the figures in prob1.4

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Basic Problems With Answers}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Basic Problems With Answers},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\begin{prob}[]{prob:1.1}
Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
\begin{equation*}
\begin{array}{ccc}
 \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
 e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
 \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-9i\pi/4}  & \sqrt{2} e^{-i\pi/4}
\end{array}
\end{equation*}
\label{prob:1.1}
\end{prob}

\begin{prob}[]{prob:1.2}
Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
-\pi < \theta \leq -\pi\)):
\begin{equation*}
\begin{array}{c{3cm}c{3cm}c{3cm}}
5 & -2 & -3i \\
\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
\end{array}
\end{equation*}
\label{prob:1.2}
\end{prob}

Every complex number \(a+ib\) can be visualized in the complex plane
\(\mathbb{C}\). It can be viewed as the point with the coordinate \((a,b)\) in
the plane or as a vector starting from \(0,0\) to the point \((a,b)\).

Also every complex number \(a+ib\) can be represented in the exponential form
conveniently through the Euler's formula \(e^{i\alpha} = \cos\alpha +
i\sin\alpha\).

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
\end{center}
\end{document}

>>>>

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
\author{Eason}
\date{\today}
\title{Problem 1.4}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Problem 1.4},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\begin{prob}[]{prob:1-4}
 Problem 1.4 Let \(x[n]\) be a signal with \(x[n]=0\) for\(n< -2\) and \(n>4\),
for each signal given below, determine the values of \(n\) for which it is
guaranteed to be zero.
\begin{eqnarray*}
\mathbf{ (a) } & & x[n-3] \\
\mathbf{ (b) } & & x[n+4] \\
\mathbf{ (c) } & & x[-n]  \\
\mathbf{ (d) } & & x[-n+2] \\
\mathbf{ (e) } & & x[-n-2]
\end{eqnarray*}
\label{prob:1-4}
\end{prob}

For the given signals \(\mathbf{(a)}\) to \(\mathbf{(e)}\), the transformations
of the variable \(n\) will change the interval in which the signals are zero.
For the convenience of calculation, we write the origin signal as:
\begin{equation*}
x[m] = 0, m< -2 \quad \mathrm{and} \quad m>4
\end{equation*}

We can visualize \(x(m)\) as below (I just give an example, you can name any
signal that satisfy \(x[m] = 0, m< -2 \ \mathrm{and} \ m>4\)):

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4.pdf}
\end{center}

\(\mathbf{(a)}:x[n-3]\)

For signal \(\mathbf{(a)}\), to get the interval where \(x[n-3] = 0\), we have:
\begin{eqnarray*}
  t=n-3 &<& -2 \\
  t=n-3 &>& 4
\end{eqnarray*}
 Then, we have \(n < 1 \ \mathrm{and} \ n > 7\) from which we can
see that the new signal is a right shift with step three relative to the origin
signal. The new signal is delayed with three.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4a.pdf}
\end{center}

\(\mathbf{(b)}:x[n+4]\)

For signal \(\mathbf{(b)}\), we have:
\begin{eqnarray*}
t=n+4&<&-2 \\
t=n+4&>&4
\end{eqnarray*}
Then, we have \(n<-6\ \mathrm{and}\ n>0\) from which we can see that the new
signal is a left shift with step four relative to the origin singal. The new
signal is advanced with four.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4b.pdf}
\end{center}

\(\mathbf{(c)}: x[-n]\)

For signal \(\mathbf{( c )}\), we have:
\begin{eqnarray*}
t=-n&<&-2 \\
t=-n&>&4
\end{eqnarray*}

Then, we have \(n>2\ \mathrm{and} \ n<-4\) from which we can see that the new
signal is a reversal of the origin signal.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4c.pdf}
\end{center}

\(\mathbf{(d)}: x[-n+2]\)

for signal \(\mathbf{(d)}\), we have:
\begin{eqnarray*}
t=-n+2&<&-2 \\
t=-n+2&>&4
\end{eqnarray*}
Then, we have \(n>4\ \mathrm{and}\ n<-2\). For \(x[-n+2]\), we can first
flip the original signal then right shift the flipped signal by 2. Notice the
contents in the brackets \(-(n+2)\). I would like treat it as \(-(n-2)\), by
which I know that the minus symbol means reversal and \(-2\) means right
shift by 2.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4d.pdf}
\end{center}

\(\mathbf{(e)}: x[-n-2]\)

For signal \(\mathbf{(e)}\), we have:

\begin{eqnarray*}
t=-n-2&<&-2 \\
t=-n-2&>&4
\end{eqnarray*}
Then, we have \(n>0 \ \mathrm{and}\ n<-6\). To get the new signal, we have
to filp the original signal first then left shift the flipped one by two.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4e.pdf}
\end{center}
\end{document}
